---
title: "clustering homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(cluster)
library(factoextra)
library(dendextend)
library(broom)

mall_data <- read_csv("data/mall_customers.csv") %>% 
  clean_names()

```

```{r}

glimpse(mall_data)
skimr::skim(mall_data)
head(mall_data)
```
Only 5 columns (4 of interest and one Unique identifier)

Good demographic information for being able to target customers, age, gender, income and spending score is good. 

More information about what spending score means would be nice. 

annual income and spending score the main columns we will be using, they are fine as they are, don't need scaled as the income already is. 


```{r}

mall_subset <- mall_data %>% 
  column_to_rownames("customer_id") %>% 
  select(annual_income_k, spending_score_1_100)
  
mall_subset

```
```{r}
mall_matrix <- mall_subset %>% 
  select(annual_income_k) %>% 
  dist(method = "euclidean")

fviz_dist(mall_matrix)

mall_kluster <- mall_matrix %>% 
  hclust(method = "complete")

plot(mall_kluster, cex = 0.1, hang = 0.1)

mall_kluster <- kmeans(mall_subset,
       centers = 4,
       nstart = 25)

tidy(mall_kluster)

augment(mall_kluster, mall_subset)

glance(mall_subset)

```

```{r}

fviz_nbclust(mall_subset,
             kmeans,
             method = "wss",
             nstart = 25)

# 3 or 4 Clusters ?

fviz_nbclust(mall_subset,
             kmeans,
             method = "gap_stat",
             nstart = 25)
# 5 Clusters ? 

fviz_nbclust(mall_subset,
             kmeans,
             method = "silhouette",
             nstart = 25)

# 5 Clusters ?
```
Based on these initial visualizations, K-value of 5 is a good place to start

```{r}


mall_subset %>% 
  ggplot()+
    aes(x = annual_income_k, 
             y = spending_score_1_100)+
  geom_point()
  
```

```{r}


mall_kluster2 <- tibble(k = 1:10) %>% 
  mutate(
    klust = map(k, ~kmeans(x = mall_subset, centers = .x, nstart = 25)),
    tidied = map(klust, tidy),
    glanced = map(klust, glance),
    augmented = map(klust, ~augment(.x, mall_subset))
  )

mall_kluster2 %>% 
  unnest(augmented) %>% 
  filter(k==5) %>% 
  ggplot()+
  aes(x = annual_income_k, y = spending_score_1_100, colour = .cluster)+
  geom_point()
```

Clustering shows 5 distinct groups, this could be very useful and i believe is a good fit for the data, however without knowing more about what the spending score is based on i couldn't answer if this current clustering is a good fit for certain.





























