---
title: "R Notebook"
output: html_notebook
---

```{r}

game_sales <- CodeClanData::game_sales


names(game_sales)

```
Looking at column names, would be good to be able to filter by:
  - year, 
  - genre, 
  - publisher, 
  - developer
  - platform
  
Where you can see their sales data, scores, rating etc. 
Multiple plots to be able to compare, ultimately looking for the top 10 
of each category only? 

Another option of sales figures over the years?

An extra option could be comparing criticscore to user score, see if there is
consistency. 

Worth looking into having an "All" option

## Make some plots. 

### This one can be for filtering by genre
```{r}
game_sales %>% 
  filter(genre == "Racing") %>% 
  filter(year_of_release == "2007") %>% 
  filter(publisher == "Nintendo") %>% 
  filter(developer == "Nintendo") %>% 
  filter(platform == "DS") %>% 
  arrange(desc(sales)) %>% 
  head(10) %>% 
  ggplot(aes(x = name, y = sales)) +
  geom_col()+
  labs(x = "Game Name",
       y = "Units sold, in millions")+
  coord_flip()


```


### A plot to display yearly sales from a specific publisher

```{r}
game_sales %>% 
  filter(publisher == "Ubisoft") %>% 
  ggplot(aes(x = year_of_release,
             y = sales))+
  geom_line()+
  labs(
    x = "Release Years",
    y = "Units sold(millions)"
  )

game_sales %>% 
  filter(publisher == "Ubisoft",
         year_of_release == 2001:2005) %>% 
  ggplot(aes(x = name, y = sales))+
  geom_col()+
  labs(x = "Game Name",
       y = "Units sold (millions)")+
  coord_flip()
  
  



```

