---
title: "Avocado Pricing Model"
output: html_notebook
---

```{r Libraries}
options(scipen = 10)

library(tidyverse)
library(janitor)
library(lubridate)
library(ggfortify)
library(GGally)

avocados <- read_csv("data/avocado.csv") %>% 
  clean_names() %>% 
  select(-x1)
```

```{r}

glimpse(avocados)
```
1. "x1" column is unique identifier for each entry, can be removed
2. "date" column for week of record, can be used to add different columns and then removed
3. "average_price" column, average selling price
4. "total_volume" column, total number of avocados sold in the week from date column
5. "PLU" columns, weight of volume of avocados in pounds
6. "bags" columns, number of mixed, pre packaged, bags of avocados sold
7. "type", conventional or organic avocados
8. "year", year of record
9. "region", region of record


# Playing about with data
```{r}



unique(avocados$region)
# Convert some region entries where possible into the larger areas to reduce number of buckets.
# With this we can bring 54 regions down to 8, then from there potentially further? 

# Main regions to be used that could be useful
avocados %>% 
  filter(region %in% c("TotalUS",
                       "California", 
                       "West", 
                       "Plains", 
                       "South Central", 
                       "Southeast", 
                       "Midsouth", 
                       "Great Lakes", 
                       "Northeast"))

# add categorical column based on date to identify seasionality
avocados %>% 
  mutate(month = month(date, label = TRUE),
         in_season = ifelse(month %in% c("Apr", "May", "Jun", "Jul", "Aug", "Sep"), TRUE, FALSE))

 # Convert weight columns to KG because we aren't madmen
avocados %>% 
  mutate(x4046 = round(x4046 * 0.453592, 2),
         x4225 = round(x4225 * 0.453592, 2),
         x4770 = round(x4770 * 0.453592, 2))

avocados %>% 
  filter(region == "TotalUS")



```


# Initial plots to check out difference in type

```{r}

avocados %>% 
  filter(region == "TotalUS") %>% 
  ggplot(aes(x = average_price, y = total_volume, colour = type))+
  geom_point()

avocados %>% 
  filter(region == "TotalUS") %>% 
  ggplot(aes(x = average_price, y = log(total_volume), colour = type))+
  geom_point()



# Shows a clear difference between the pricing/volume and the type,
# I would say that this shows that we should be looking at the data 
# for both types sepererately. However the code can be used for both the same way

```

Using GGpairs to check how other factors impact the two types

```{r, message=FALSE, warning=FALSE}


avocados %>% 
select(-date) %>% 
    filter(region=="TotalUS") %>% 
  ggpairs()

# Initially from looking at ggpairs results, I would be wanting to try and 
# combine bags and PLU scores into a single bucket for more useful comparison


```

