---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)

card_base <- read_csv("data/CardBase.csv")
customer_base <- read_csv("data/CustomerBase.csv")
fraud_base <- read_csv("data/FraudBase.csv")
transaction_base <- read_csv("data/TransactionBase.csv")

view(card_base)
view(customer_base)
view(fraud_base)
view(transaction_base)
```


#1.1


# Question 1


```{r}

card_base <- clean_names(card_base)
customer_base <- clean_names(customer_base)
fraud_base <- clean_names(fraud_base)
transaction_base <- clean_names(transaction_base)

# cleaned names

```

# Question 2

Join the data containing card details and customer details by customer id, so that all records of card details and any matching records in customer details are kept. Before you run the code, think about how many rows you expect to see after joining.

```{r}

#500 rows in card base, should be 500 after


card_details <- left_join(card_base, customer_base, by = c("cust_id" = "cust_id"))

card_details

```

# Question 3

Join the data containing fraud details with transaction details so all rows of both tables are kept. What does the resulting row number tell you?

```{r}

transactions <- full_join(transaction_base, fraud_base, by = c("transaction_id" = "transaction_id"))

# 10,000 rows was the number of rows in transaction base, everything is kept, the fraud_flag entries that weren't added from fraud base are NA, could be removed if we just wanted to see the extra info for fraud transactions

transactions

```

# Question 4

Join the data containing card details with transaction details so rows from the first which have matching ones in the second are returned, but only return rows in the first table once.


```{r}

semi_join(card_details, transactions, by = c("card_number" = "credit_card_id"))



```

#1.2

# Question 1

Read in hat_observations and separate observation into two columns, hat_colour and hat_type. 

```{r}

hats <- read_csv("data/hat_observations.csv")

hats <- hats %>% 
  separate(col = observation,
           into = c("hat_colour", "hat_type"), sep = ",")

hats

```

# Question 2

Unite day, month, and year columns into a column called date using a suitable separator. Then find the date where the most berets were observed.

```{r}


hats <- hats %>% 
  unite(col = "date",
        c("day", "month", "year"), sep = "/")

hats

hats %>% 
  group_by(hat_type, date) %>% 
  summarise(total_hats = sum(observation_count)) %>% 
  arrange(desc(total_hats))
  
# Total Berets seen on 18th June is 11, 9 white and 2 purple
  
```

# Extension 

#2.1 

```{r}

#Bring everything across from the previous question as a full join instead of semi
right_join(card_details, transactions, by = c("card_number" = "credit_card_id")) %>% 
  # this gives 10,000 entries and 12 columns
  drop_na()
  # this leaves 109 rows and 12 columns

```

# 2.2

Question 2

Read in exam_scores and transform it into long format with two new columns exam_question and score. Then, using separate and select, remove superfluous information from the values in exam_question


```{r}

exams <- read_csv("data/exam_scores.csv")

exams %>% 
  pivot_longer(cols = starts_with("exam_Q"),
               names_to = "exam_question",
               values_to = "score") %>%
  separate(col = exam_question,
           into = c("exam", "question_number"), sep = "_Q") %>% 
  select(id, question_number, score)
  

```

