---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

cc_info <- read_csv("data/code_clan_info.csv")
cc_tweets <- read_csv("data/code_clan_tweets.csv")
```
# Question 1

Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names

```{r}

nrow(cc_tweets)
# 234 Rows

ncol(cc_tweets)
# 27 columns

names(cc_tweets)

view(cc_tweets)

```

# Question 2

Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}

cc_tweets %>% 
  count(is_quote)

cc_tweets %>% 
  filter(is_quote == FALSE) %>% 
  mutate(total_favourites = sum(favorite_count)) %>% 
  count(total_favourites)

## Total favorites 425 over 227 tweets that weren't quoted

```

# Question 3

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}

cc_tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  mutate(avg_retweet = mean(retweet_count)) %>% 
  count() 
  

```

# Question 4

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}

cc_tweets %>% 
  select(media_type, favorite_count) %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>%
  mutate(total_likes = sum(favorite_count)) %>% 
  arrange(desc(total_likes)) %>% 
  count(total_likes)

```


# Question 5
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).


```{r}

tweet_text <- cc_tweets %>%
  pull(text)

tweet_text <- tweet_text %>% 
  # Do not run str_split on its own, it will take forever
  str_split("") %>% 
  lengths()

mean_tweets <- tweet_text %>% 
  mean()
  
 mean_tweets 
  

```



# Question 6

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.


```{r}

view(cc_info)

tweets_info <- left_join(cc_tweets, cc_info, by = c("tweet_id"))

```



# Question 7

From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}

codeclan_hashtags <- tweets_info %>% 
  select(tweet_id, hashtags)

codeclan_hashtags %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  drop_na()


```

