---
title: "Text Mining Homework"
output: html_notebook
---

Text Mining Homework

# MVP

Using the dataset austen_books() from the package janeastenr:
  1. Find the most common words in both Pride & Prejudice and Sense & Sensibility
  2. Find the most common words in both Pride & Prejudice and SEnse & Sensibility,         not including stop words
  3. Find the most common sentiment words in both P & P and S & S
  
  
```{r}
library(tidytext)
library(tidyverse)
library(janeaustenr)
```



1. Find the most common words in both Pride & Prejudice and Sense & Sensibility

```{r}

austen_books <- janeaustenr::austen_books()

austen_df <- austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text)

austen_df %>% 
  group_by(book) %>% 
  count(word, sort = TRUE)

```

2. Find the most common words in both Pride & Prejudice and Sense & sensibility, not including stop words

```{r}
austen_books <- janeaustenr::austen_books()

austen_df <- austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text)

austen_df %>% 
  anti_join(stop_words) %>% 
  group_by(book) %>% 
  count(word, sort = TRUE)


```


3. Find the most common sentiment words in both Pride & PRejudice and Sense & Sensibility

```{r}

austen_books <- janeaustenr::austen_books()

austen_df <- austen_books %>% 
  filter(book %in% c("Sense & Sensibility", "Pride & Prejudice")) %>% 
  unnest_tokens(word, text)

austen_df %>% 
  inner_join(get_sentiments("nrc")) %>% 
  group_by(book, sentiment) %>% 
  count(sentiment, sort = TRUE)

```

# Extension 

Taking the results above. Can you create a plot which visualises the differences between the books? 

```{r}

austen_df %>%
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  group_by(book, sentiment) %>% 
  count(sentiment) %>% 
  ggplot()+
  aes(x = sentiment, y = n, fill = book)+
  geom_col(position = "dodge")
```





















