---
title: "Distributions Homework"
output: html_notebook
---

#   MVP
## Question 1

Load the data, clean_names and explore

```{r}
library(janitor)
library(tidyverse)

phone_data <- read_csv("data/20190928-items.csv") %>% 
  clean_names()

names(phone_data)
glimpse(phone_data)
```

## Question 2
Find the brand with the highest numbers of phones in the dataset
```{r}
phone_data %>% 
  group_by(brand) %>% 
  count() %>% 
  arrange(desc(n))


# Samsung has the most phones
```

## Question 3
Plot the distribution of phone ratings as a probability density, overlaying a 
fitted normal distribution. Do you think the normal distribution provides a good
model of these ratings?

```{r}

samsung_phone_data <- phone_data %>% 
  filter(brand == "Samsung")

samsung_phone_data <- samsung_phone_data %>% 
  select(rating, total_reviews)

avg_samsung_rating <- samsung_phone_data %>% 
  summarise(avg_rating = mean(rating)) %>% 
  pull()
# I am aware that these could have just been mutated on but i decided to store
# on their own
sd_samsung_rating <- samsung_phone_data %>% 
  summarise(sd_rating = sd(rating)) %>% 
  pull()

samsung_phone_data %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white") +
  stat_function(
    fun = dnorm,
    args = list(
      mean = avg_samsung_rating,
      sd = sd_samsung_rating
    ),
    col = "seagreen",
    size = 1.2
  )


# normal distribution looks good for these ratings as the curve overall matches 
# the shape of the histogram

```

## Question 4

```{r}
# Taken from notes

# Calculating prorortions within one standard deviation of the mean

samsung_phone_data %>% 
  filter(
    rating >= avg_samsung_rating - sd_samsung_rating) %>%
  filter(
    rating <= avg_samsung_rating + sd_samsung_rating) %>% 
  summarise(prop_within_1sd = n() / nrow(samsung_phone_data)
  )

# Calculating proportions within two standard deviations of the mean

samsung_phone_data %>% 
  filter(
    rating >= avg_samsung_rating - 2 * sd_samsung_rating) %>%
  filter(
    rating <= avg_samsung_rating + 2 * sd_samsung_rating) %>% 
  summarise(prop_within_2sd = n() / nrow(samsung_phone_data)
  )

# Calculating proportions within three standard deviations of the mean

samsung_phone_data %>% 
  filter(
    rating >= avg_samsung_rating - 3 * sd_samsung_rating) %>%
  filter(
    rating <= avg_samsung_rating + 3 * sd_samsung_rating) %>% 
  summarise(prop_within_3sd = n() / nrow(samsung_phone_data)
  )
```

## Summary from Notes

For a normal distribution, expect 68% of values to fall within one standard deviation of the mean. Here, 79% of ratings are within this range, so our distribution is slightly too central.

Adding another standard deviation to either side should increase the proportion of values by 27% to 95% overall in a normal distribution. Our distribution adds 13%, going to 92% overall, so there are too few values in the range from one- to two standard deviations.

Finally, in a normal distribution, adding a further standard deviation to either side should increase the proportion of values by 4.7% to 99.7% overall. Our distribution adds 6% to 98%, so this is pretty close. 