---
title: "R Notebook"
output: html_notebook
---


##Read in library of tidyverse and the data for the task
```{r}
library(tidyverse)

#save as a variable to be used later
movie_data <- read.csv("data/movies.csv")


```

## Question 1
- After you’ve read in the data and assigned it to a variable with a useful name, investigate it. 
- Write down some ideas for what you could do to further investigate/clean this data using what you’ve learned today (no need to code it though, just jot down thoughts and ideas). 
- Feel free to also write down any general thoughts you get looking at the data - this task is just to get you thinking about data and data cleaning/prepping.

##Q1 - Notes
- Nearly 5000 rows, lots of information to sort
- Budget Column could be made smaller, lots of 0's makes it visually harder to read
- are there even any differences between original_title and title?
- could do budget - revenue to find actual profit
- what does popularity mean, whats the value out of?

##Question 2

A lot of interesting stuff in there! But for now, we are only interested in the movies’ titles, their runtime as well as their budget. Select the three columns that contain this information and save them into a new variable called movies_selected. Hint: you will have to make a choice between original_title and title

```{r}

##Choosing title over original title for personal preference

movies_selected <- movie_data %>% 
  select(title, runtime, budget)


movies_selected
```



## Question 3
Ok, now take your subsetted data movies_selected, and count the number of missing values in each column.

```{r}

##Struggled with remembering how to do this
movies_selected %>% 
  summarise(
    across(
      everything(), ~ sum(is.na(movies_selected))
    )
  )


#Error Code   You most likely meant: `across(everything(),
 #everything() ~ sum(is.na(movies_selected)))`. 
 # Was missing a comma after everything

  



```


##Question 4
There’s not too many NAs, but there are actually quite a few movies with a runtime of 0 in this dataset. Since it’s impossible for a movie to have a runtime of 0, use the function na_if to convert runtimes of length 0 into NAs. Save this into a new variable called movies_runtime. Then count how many missing values there are now in the column runtime.

```{r}
movies_runtime <- movies_selected %>% 
  mutate(runtime = na_if(runtime, 0))


## count, tried to arrange but NA always stayed at the end, 37 NAs now

movies_runtime %>% 
  count(runtime)
  

```

##Question 5
Impute the missing values in runtime with the median runtime using coalesce and save this into a new variable called movies_imputed. There should now be no missing values in the column runtime - check this to make sure.

```{r}

# turn the Na values into the median value using coalesce and then save as a variable
movies_imputed <- movies_runtime %>%
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed %>% 
  count(runtime) # shows no Na values in runtime
  
```

##Question 6
Finally, use the slice_min and slice_max functions on movies_imputed to get the movies with the 10 shortest and 10 longest runtimes

```{r}

?slice # to remember how to use slice

#shortest movies
movies_imputed %>%
  arrange(.data = movies_imputed, runtime) %>% 
  slice_min(runtime, n = 10)

#longest movies
movies_imputed %>% 
  arrange(.data = movies_imputed, runtime) %>% 
  slice_max(runtime, n = 10)
```

##Question 7 
Using the if_else function, impute anything with a budget below $100 with the median budget. Overwrite your movies_imputed so it contains the new budget values.

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget <= 100, median(budget), budget)) %>% 
  arrange(desc(budget))

# double check to see the median budget

#movies_imputed %>% 
 # select(title, budget) %>% 
  #mutate(budget_median = median(budget)
  #)

movies_imputed

```

## Extension Question 1
Using case_when, create a new column called budget_type and label budgets as follows:

    Budgets below 12 million as ‘Small budget’
    Budgets between 12 and 40 million as ‘Medium budget’
    Budgets 40 millions and above as ‘Big budget’

Save this into a new variable called movie_budgets.

```{r}

##create new column and assign values to the different budgets
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(
    budget < 12e6 ~ "Small budget",
    budget > 40e6 ~ "Big budget",
    TRUE ~ "Medium budget"
  ))

# double check the total number of different movies based on budget type
movie_budgets %>% 
  count(budget_type)

```

## Extension Question 2

Take the original dataset with all the variables. Using across and where, summarise the number of missing values, first across all columns of type character, and then across all columns of type numeric.