---
title: "R Notebook"
output: html_notebook
---

# Advanced ggplot2 Homework

## 1.1 Learning Objectives

  - Practice making plots with ggplot2
  - Create your own theme and use it with plots
  
```{r}
library(CodeClanData)
library(tidyverse)


```
# 2 MVP

## 2.1 Part 1

### Question 1 
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset

```{r}

qb_revenue_breakdown %>% 
  ggplot(aes(x = Product, y = Revenue, fill = Year)) +
  geom_col(position = "dodge") + 
  labs(
    title = "Source of Revenue over past two years",
    x = "Revenue Sources",
    y = "Revenue Generated"
  )+
  hw_theme +
  scale_fill_manual(values = col_scheme)

```

### Question 2
Make a line chart showing monthly sales of the "flagship product" - the 'KwikBit Unit 1' - over the last year. This data is inside qb_monthly_sales, but you will need to use filter or subset

```{r}

qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = Date, y = Amount))+
  geom_line(colour = "#bd7040",
            size = 1)+ 
  labs(
    title = "Monthly sales of KwikBit Unit 1 over the last year",
    x = "Timeframe",
    y = "Monthly Sales"
  )+
  hw_theme

```

### Question 3
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales

```{r}

qb_monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = Date, y = Amount, group = Cashflow, colour = Cashflow)) +
  geom_line() + 
   hw_theme
  
```

### Question 4
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot(use geom_area). This data is in qb_competitors

```{r}

qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, fill = Company)) +
  geom_area()+
   hw_theme+
  scale_fill_manual(values = col_scheme)


```

### Question 5
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines. 

```{r}

qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, group = Company, colour = Company)) +
  geom_line()+
  geom_point() + 
   hw_theme+
  scale_fill_manual(values = col_scheme)
```

### Question 6
Now the company wants to compare the number of steps that their device counts vs their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data. 

```{r}

qb_device_data %>%
  mutate(time = (hours * 60) + mins) %>% 
  ggplot(aes(x = time, y = counts, group = id, colour = device))+
  geom_line()+
  facet_wrap(~device) + 
   hw_theme+
  scale_fill_manual(values = col_scheme)
  

```

```{r}

hwl <- list(col_scheme + hw_theme)

hw_theme <- theme(
  panel.background = element_rect("white"),
  axis.line =  element_line("#50434F"),
  panel.grid = element_line("#dcd5dc"),
  text = element_text(size = 12),
  axis.text = element_text(size = 10),
  title = element_text(size = 14)
  ) 
)

col_scheme <- c("#f9a472", "#bd7040", "#e89Fe9", "#b6a7b5", "#50434f")
```

