---
title: "Linear Regression Homework"
output: html_notebook
---

# MVP 

  - Load the data into a dataframe project
  
```{r Libraries}
library(tidyverse)
library(broom)
library(modelr)
library(ggfortify)

proj_data <- read_csv("data/project_management.csv")


```

  - Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.
  
```{r}
proj_data %>% 
  ggplot(aes(x = estimated_length, y = actual_length))+
  geom_point()

```

- Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain. 

```{r}

cor(proj_data$estimated_length, proj_data$actual_length)

# 0.8046597

```

  - Perform a simple linear regression using actual length as the dependent variable, and estimated length as the independent variable. Save the model object to a variable
  
```{r}

model <- lm(formula = actual_length ~ estimated_length, data = proj_data)

```
  
  - Interpret the regression coefficient of estimated_length 
  (ie. Slope, gradient) you obtain from the model. How do you interpret 
  the r2 value reported by the model?


```{r}
model

tidy(model)
glance(model)


```
The estimated length increases by 1.223 for every 1 of the actual length. 

The r2 value reported by the model of 0.647 would show a good rate at which the model fits the data

  - Is the relationship statistically significant? Remember, to assess this you 
  need to check the p-value of the regression coefficient(or slope/gradient). 
  But you should first check the regression diagnostic plots to see if the 
  p-value will be reliable(don't worry about any outlier points you see in the
  diagnostic plots, we'll return to them in the extension.)
  
```{r}

autoplot(model)
```

Residuals vs Fitted, plot looks fine as it stays around 0 , only going out to -2.5.

Normal Q-Q, plot looks fine as all of the points lie very clsoe to the line

Scale-Location, plot looks fine as it is all above the x-axis with only minor fluctation

Overall these show that the p-value should be reliable


  