---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(gtools)
library(janitor)

source("/CodeClan/codeclan_work/week_06/day_01/prob.R")

titanic_data <- read.csv("data/titanic.csv") %>% 
  clean_names()

titanic_classes <- unique(titanic_data$class)
```

```{r}
passengers <- titanic_data %>% 
  filter(class %in% c("1st", "2nd", "3rd"))

crew <- titanic_data %>% 
  filter(class %in% c("deck crew", "engineering crew", "restaurant staff", "victualling crew"))

crew_survived <- crew %>% 
  filter(survived == "yes")

passenger_survived <- passengers %>% 
  filter(survived == "yes")

prob_crew_survive <- nrow(crew_survived) / nrow(crew)
# 23%

prob_passenger_survived <- nrow(passenger_survived) / nrow(passengers)
# 37% Chance

# Passengers had a higher chance of survival

```

#   1.2
## Question 1
### If I roll a six-sided dice once, what is the probabilty of getting a number 
less than 5


```{r}
# 4 out of the 6 options are less than 5

less_than_5_dice <- 4/6

```

## Question 2
How many outcomes are there in the sample space of an experiment in which we
toss three dice?

```{r}

q2_three_dice <- rolldie(3) %>% 
  nrow()

# 216 potential outcomes

```

## Question 3
In an experiment where we roll four dice:

```{r}
# How many outcomes are in the event where the 
# total of the four dice equals 5, 6, 7

four_dice <- rolldie(4)

four_dice <- four_dice %>% 
  mutate(totals = X1+X2+X3+X4)
  
less_than_eight_totals <- four_dice %>% 
  filter(totals %in% c(5:7))
# 34  outcomes

# What is the probability of this event?

prob_less_than_eight_four_dice <- nrow(less_than_eight_totals) / nrow(four_dice)

# 0.069 %

```

## Question 4
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

# Fucking low as hell i assume

```{r}
heights_sample <- c("188", "176", "135", "194", "166")
# There can be only one correct option for this, therefore it will be probability based on 1/ total possible combinations

heights_combos <- permutations(5, 5, heights_sample)

prob_height_order <- 1 / nrow(heights_combos)

# 0.08% chance
```

## Question 5
I roll six dice:
```{r}
# What is the probability i see the numbers 6,5,4,3,2,1 in order on the dice, left to right?
s_six_dice <- rolldie(6)

# as we know its a list of every possible combination, only one correct answer can exist

prob_dice_order <- 100 * (1 / nrow(s_six_dice))
# 0.002% chance

# What is the probability i see one each of the numbers on the dice, regardless of order

any_order_nums <- s_six_dice %>% 
  mutate(pattern =  isin(., c("1", "2", "3", "4", "5", "6"))) %>% 
  filter(pattern == TRUE)
  
prob_any_order_all <- nrow(any_order_nums) / nrow(s_six_dice)

# 1.5% chance
```

# Question 6
 If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades.
 
  - Spades/Clubs are half the pack, if you are measuring what are the chances a black card is a spade, surely it would be 50/50 as all black cards are either spades or clubs and they have an equal amount?
  - If you are measuring what is the chance of a card being drawn that is spades then it would be 1/4 as all cards are the same in a full deck? 