---
title: "R Notebook"
output: html_notebook
---

```{r Libraries}
library(tidyverse)
library(janitor)
library(ggfortify)
library(GGally)
# install.packages("raster")
library(raster)
library(leaflet)

housing <- read_csv("data/housing_prices.csv")
```

Notes: 

  - What does one row represent? An aggregate of a district in California
  - Some variables are raw sums, some are "stats", like averages
  --> do some feature engineering  variable transformation to get more "stats" 
      that are meaningful to me about these houses
  
Lets do some "feature engineering"
  - The data set we start with is te "raw materials"
  - We can use those to make more meaning, aid interpretation
  
```{r}

housing <- housing %>% 
  mutate(bedrooms_per_house = total_bedrooms / households,
         rooms_per_house = total_rooms / households,
         people_per_house = population / households,
         bedrooms_per_person = bedrooms_per_house / people_per_house,
         rooms_per_person = total_rooms / population,
         bedrooms_per_room = total_bedrooms / total_rooms,
         non_bedrooms_per_house = rooms_per_house - bedrooms_per_house,
  )

```

 * Extra idea: start using long & lats to make more meaning
 --> joining to external city coordinate data, creating labels, flags, or 
     things like "distance to city"

Let's explore the relationships between teh variables - what looks like 
it influences price?

```{r, message = FALSE, warning = FALSE}
ggpairs1 <- housing %>% 
  select(median_house_value,
         housing_median_age,
         median_income,
         ocean_proximity) %>% 
  ggpairs()

ggpairs1

ggpairs2 <- housing %>% 
  select(median_house_value,
         total_rooms,
         rooms_per_house,
         total_bedrooms,
         bedrooms_per_house) %>% 
  ggpairs()

ggpairs2

ggpairs3 <- housing %>% 
  select(median_house_value,
         households,
         population,
         people_per_house,
         total_rooms,
         rooms_per_house) %>% 
  ggpairs()

ggpairs3

```

```{r}

raster_house_value <- rasterFromXYZ(housing %>% 
  dplyr::select(longitude, latitude, median_house_value), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")


raster_pop <- rasterFromXYZ(housing %>% 
  dplyr::select(longitude, latitude, population), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")


plot(raster)

pal_pop <- colorNumeric(c("transparent", "red"), values(raster_pop),
  na.color = "transparent")
pal_house_value <- colorNumeric(c("yellow", "blue"), values(raster_house_value),
  na.color = "transparent")

leaflet() %>% 
  addTiles() %>% 
  addRasterImage(raster_house_value,
                 colors = pal_house_value,
                 opacity = 0.7) %>% 
  addRasterImage(raster_pop,
                 colors = pal_pop,
                 opacity = 0.7)


%>% 
   addLegend(pal = pal_house_value, values = values(raster_house_value),
    title = "House Values")


```

Log Transformations

```{r}
ggplot(housing, aes(x = median_income))+
  geom_histogram()

ggplot(housing, aes(x = log(median_income)))+
  geom_histogram()

ggplot(housing, aes(x = median_house_value))+
  geom_histogram()

ggplot(housing, aes(x = log(median_house_value)))+
  geom_histogram()


```




# 1 MVP
## 1 Load the housing_prices.csv data set and undertake an initial exploration of the data

```{r}

glimpse(housing)
summary(housing)
head(housing)

housing %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

# total bedrooms has all the NA values
```

##2 
  We expect the total_rooms of houses to be strongly correlated 
  with total_bedrooms. Use ggpairs() to investigate correlations between
  these two variables
  
```{r, message = FALSE, warning = FALSE}

ggpairs(housing)

# correlation value: 0.934 *** VERY Strongly correlated

# Notes from homework: 

ggpairs(housing[,c("total_rooms", "total_bedrooms")])

# Really useful to reduce the size of the graph/speed of loading 

# Alternate method by tidyverse methods:

housing %>% 
  select(total_bedrooms, total_rooms) %>% 
  ggpairs()


```
  
##3 So, we do find significant correlations. Let's drop total_bedrooms from 
the dataset, and use only total_rooms going forward. 

```{r}
housing <- housing %>% 
  select(-total_bedrooms)
```

##4
We are interesting in developing a regression model for the median_house_value 
of a house in terms of the possible predictor variables in the dataset.
  1. Use ggpairs() to investigate correlations between median_house_value and
     the predictors
  2. Perform further ggplot visualisations of any significant correlations

```{r, message = FALSE, warning = FALSE}
#1 
ggpairs(housing)


#2 

housing %>% 
  ggplot(aes(x = median_house_value, y = total_rooms))+
  geom_point()


housing %>% 
  ggplot(aes(x = median_house_value, y = ocean_proximity))+
  geom_boxplot()

housing %>% 
  ggplot(aes(x = median_house_value, y = population))+
  geom_point()

housing %>% 
  ggplot(aes(x = median_house_value, y = households))+
  geom_point()

housing %>% 
  ggplot(aes(x = median_house_value, y = median_income))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

housing %>% 
  ggplot(aes(x = median_house_value, y = housing_median_age))+
  geom_point()

```

##5 
Shortly we may try a regression model to fit the categorical predictor ocean_proximity.
Investigate the level of ocean_proximity predictos. 
How many dummy variables do you expect to get from it?

```{r}

unique(housing$ocean_proximity)

# We can get 4 dummy variables from this as there are 5 variables within ocean_proximity

```

##6 Start with simple linear regression. Regress median_house_value on median_income and check the regression diagnostics.

```{r}

lm1 <- lm(median_house_value ~ median_income, housing)

lm1
summary(lm1)

autoplot(lm1)
```

##7 Add another predictor of your choice. Check your assumptions, diagnotstics, and interpret the model

```{r}

lm2 <- lm(median_house_value ~ median_income + total_rooms, housing)

lm2
summary(lm2)
autoplot(lm2)
```
## Extension

##8 Try adding an interaction between log(median_income) and your chosen categorical
    predictor. Do you think this interaction term is statisticlaly justified?
    
```{r}




```

