---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(sf)
library(scales)

healthboards_data <- read_csv("data/opendata_inc9620_hb.csv") %>% 
  clean_names()

cancer_demographic_data <- read_csv("data/opendata_inc9620_scotland.csv") %>% 
  clean_names()

hb_map <- st_read("data/SG_NHS_HealthBoards_2019/SG_NHS_HealthBoards_2019.shp")
hb_map$HBName <- as.character(hb_map$HBName)
hb_map$HBName <-  str_c("NHS ", hb_map$HBName)

view(healthboards_data)

```

```{r}

unique(healthboards_data$hb)
unique(cancer_demographic_data$country)

head(healthboards_data)

healthboards_data %>% 
  group_by(hb, year) %>% 
  mutate(avg_yearly_incidences = mean(incidences_all_ages)) %>% 
  ggplot(aes(x = year, y = avg_yearly_incidences, group = hb, colour = hb)) +
  geom_line()+
  facet_wrap(~sex)

cancer_demographic_data <- cancer_demographic_data %>% 
  pivot_longer(cols = starts_with("incidences_a"), 
               names_to = "incidence_age_range",
               names_prefix = c("incidences_age", "incidences_"),
               values_to = "incidences_per_age_range") %>% 
  pivot_longer(cols = starts_with("incidence_r"),
               names_to = "incidence_rate_age",
               names_prefix = "incidence_rate_age",
               values_to = "incidence_rate_age_range")

cancer_age_data <- cancer_demographic_data %>% 
  select(cancer_site, sex, year, crude_rate, incidence_age_range, 
         incidences_per_age_range, incidence_rate_age, incidence_rate_age_range)

cancer_age_data %>% 
  filter(sex == "Male") %>% 
  group_by(incidence_age_range) %>% 
  summarise(incidences_per_age_range)
  
```

What do I want to see from this data set, has the gender, age splits and what 
kind of cancer. 

most common cancer by age with a gender split

Want to see how the Borders compares with other areas

 - Does the borders stand out from any other region for an increase/decrease
 - Check by demographic, age group and gender? 
 
 TODO: 
 Change names on map to add "NHS" to regions,
 Add NHS region names to the datasets so it isn't just the code. 
 
 Use map as a summary for cases of all ages, then go into detail for how that 
 is split by age group? Then show the difference in gender?
      
```{r}

healthboards_data <- healthboards_data %>% 
  select(hb, cancer_site, sex, year, incidences_all_ages, crude_rate) %>% 
  mutate(hb = recode(hb, 
                     S08000015 = "NHS Ayrshire and Arran",
                     S08000016 = "NHS Borders",
                     S08000017 = "NHS Dumfries and Galloway",
                     S08000018 = "NHS Fife",
                     S08000019 = "NHS Forth Valley",
                     S08000020 = "NHS Grampian",
                     S08000021 = "NHS Greater Glasgow and Clyde",
                     S08000022 = "NHS Highland",
                     S08000023 = "NHS Lanarkshire",
                     S08000024 = "NHS Lothian",
                     S08000025 = "NHS Orkney",
                     S08000026 = "NHS Shetland",
                     S08000027 = "NHS Tayside",
                     S08000028 = "NHS Western Isles",
                     S08000029 = "NHS Fife",
                     S08000030 = "NHS Tayside",
                     S08000031 = "NHS Greater Glasgow and Clyde",
                     S08000032 = "NHS Lanarkshire"))

cancer_by_region <- healthboards_data %>% 
  filter(cancer_site == "All cancer types") %>% 
  group_by(hb) %>%
  mutate(total_cancer_incidences = sum(incidences_all_ages))

hb_map$cancer_incidences <- cancer_by_region$total_cancer_incidences[match(hb_map$HBName, cancer_by_region$hb)]
hb_map$crude_rate <- cancer_by_region$crude_rate[match(hb_map$HBName, cancer_by_region$hb)]

options(scipen = 10)

hb_map %>% 
  ggplot(aes(fill = cancer_incidences))+
  geom_sf()+
  theme_void()+
  scale_fill_gradient2(
    name = "Incidences"
  )+
  labs(
    title = "Total cancer incidences by NHS Region"
  )

hb_map %>% 
  ggplot(aes(fill = crude_rate))+
  geom_sf()+
  theme_void()+
  scale_fill_gradient2(
    name = "Crude Rate"
  )+
  labs(
    title = "Crude rate of cancer incidences per 100,000"
  )



```

```{r, echo = FALSE, warning = FALSE, fig.}

healthboards_data %>% 
  filter(cancer_site != "All cancer types",
         hb == "NHS Borders",
         sex == "Male") %>% 
  group_by(cancer_site) %>%
  mutate(total_incidences = sum(incidences_all_ages)) %>% 
  slice_max(n = 1, order_by = total_incidences, with_ties = FALSE) %>% 
  arrange(desc(total_incidences)) %>% 
  head(10) %>% 
  ggplot(aes(x = cancer_site, y = total_incidences, fill = sex))+
  geom_col(fill = "darkgreen")+
  coord_flip()+
  labs(
    x = "Type of Cancer",
    y = "Incidences",
    title = "Cancer Incidences in the Borders"
  )+
  theme_classic()

healthboards_data %>% 
  filter(cancer_site != "All cancer types",
         hb == "NHS Borders",
         sex == "Female") %>% 
  group_by(cancer_site) %>%
  mutate(total_incidences = sum(incidences_all_ages)) %>% 
  slice_max(n = 1, order_by = total_incidences, with_ties = FALSE) %>% 
  arrange(desc(total_incidences)) %>% 
  head(10) %>% 
  ggplot(aes(x = cancer_site, y = total_incidences, fill = sex))+
  geom_col(fill = "darkorchid")+
  coord_flip()+
  labs(
    x = "Type of Cancer",
    y = "Incidences",
    title = "Cancer Incidences in the Borders"
  )+
  theme_classic()
```

```{r}

unique(healthboards_data$hb)

healthboards_data %>% 
  filter(hb == "NHS Borders",
         cancer_site == "All cancer types",
         sex != "All") %>%
  ggplot(aes(x = year, colour = sex, y = incidences_all_ages))+
  geom_line()+
  labs(x = "Year",
       y = "Incidences",
       title = "Cancer Incidences in the Borders over the years")+
  theme_classic()


```

```{r}

cancer_age_data %>% 
  group_by(incidence_age_range) %>%
  filter(sex != "All",
         incidence_age_range != "incidences_all_ages") %>% 
  ggplot(aes(x = incidence_age_range, y = incidences_per_age_range))+
  geom_col()+
  coord_flip()+
  facet_wrap(~sex)+
  theme_classic()+
  labs(x = "Age Range",
       y = "Incidences",
       title = "Cancer Incidences by Age")

cancer_age_data %>% 
  filter(incidence_age_range != "incidences_all_ages") %>% 
  ggplot(aes(x = year, y = incidences_per_age_range))+
  geom_line()

```

