---
title: "NHS Borders Cancer Analysis"
output:
  html_document:
    df_print: paged
---

The Brief: 

In order to help inform the planning for provision of cancer treatment services
in NHS Borders, we would like to gain better understanding of the incidence of 
cancer in NHS Borders.

```{r Libraries and Formatting, echo=FALSE, message=FALSE, warning=FALSE}
#Datasets and Libraries

library(tidyverse)
library(janitor)
library(sf)
library(scales)

healthboards_data <- read_csv("data/opendata_inc9620_hb.csv") %>% 
  clean_names()

cancer_demographic_data <- read_csv("data/opendata_inc9620_scotland.csv") %>% 
  clean_names()


invisible(capture.output(hb_map <- st_read("data/SG_NHS_HealthBoards_2019/SG_NHS_HealthBoards_2019.shp")))
hb_map$HBName <- as.character(hb_map$HBName)
hb_map$HBName <-  str_c("NHS ", hb_map$HBName)


cancer_demographic_data <- cancer_demographic_data %>% 
  pivot_longer(cols = starts_with("incidences_a"), 
               names_to = "incidence_age_range",
               names_prefix = c("incidences_age", "incidences_"),
               values_to = "incidences_per_age_range") %>% 
  pivot_longer(cols = starts_with("incidence_r"),
               names_to = "incidence_rate_age",
               names_prefix = "incidence_rate_age",
               values_to = "incidence_rate_age_range")

cancer_age_data <- cancer_demographic_data %>% 
  select(cancer_site, sex, year, crude_rate, incidence_age_range, 
         incidences_per_age_range, incidence_rate_age, incidence_rate_age_range)

healthboards_data <- healthboards_data %>% 
  select(hb, cancer_site, sex, year, incidences_all_ages, crude_rate) %>% 
  mutate(hb = recode(hb, 
                     S08000015 = "NHS Ayrshire and Arran",
                     S08000016 = "NHS Borders",
                     S08000017 = "NHS Dumfries and Galloway",
                     S08000018 = "NHS Fife",
                     S08000019 = "NHS Forth Valley",
                     S08000020 = "NHS Grampian",
                     S08000021 = "NHS Greater Glasgow and Clyde",
                     S08000022 = "NHS Highland",
                     S08000023 = "NHS Lanarkshire",
                     S08000024 = "NHS Lothian",
                     S08000025 = "NHS Orkney",
                     S08000026 = "NHS Shetland",
                     S08000027 = "NHS Tayside",
                     S08000028 = "NHS Western Isles",
                     S08000029 = "NHS Fife",
                     S08000030 = "NHS Tayside",
                     S08000031 = "NHS Greater Glasgow and Clyde",
                     S08000032 = "NHS Lanarkshire"))

cancer_by_region <- healthboards_data %>% 
  filter(cancer_site == "All cancer types") %>% 
  group_by(hb) %>%
  mutate(total_cancer_incidences = sum(incidences_all_ages))

hb_map$cancer_incidences <- cancer_by_region$total_cancer_incidences[match(hb_map$HBName, cancer_by_region$hb)]
hb_map$crude_rate <- cancer_by_region$crude_rate[match(hb_map$HBName, cancer_by_region$hb)]

options(scipen = 10)
```


From the brief the main areas I wanted to look at were:
<details>
<summary>  - How the borders compares with other healthboard regions</summary>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
hb_map %>% 
  ggplot(aes(fill = cancer_incidences))+
  geom_sf()+
  theme_void()+
  scale_fill_gradient2(
    name = "Incidences"
  )+
  labs(
    title = "Total cancer incidences by NHS Region"
  )

hb_map %>% 
  ggplot(aes(fill = crude_rate))+
  geom_sf()+
  theme_void()+
  scale_fill_gradient2(
    name = "Crude Rate"
  )+
  labs(
    title = "Crude rate of cancer incidences per 100,000 people"
  )

```

Side note: Approx 110,200 people in NHS Borders compared with over 1,196,000 in 
NHS Greater Glasgow & Clyde

</details>  


<details>
<summary>  - Difference in cancer incidences across different demographics, including sex and age </summary>


```{r echo=FALSE, fig.show='hold', warning=FALSE, out.width='50%'}

healthboards_data %>% 
  filter(cancer_site != "All cancer types",
         hb == "NHS Borders",
         sex == "Male") %>% 
  group_by(cancer_site) %>%
  mutate(total_incidences = sum(incidences_all_ages)) %>% 
  slice_max(n = 1, order_by = total_incidences, with_ties = FALSE) %>% 
  arrange(desc(total_incidences)) %>% 
  head(10) %>% 
  ggplot(aes(x = cancer_site, y = total_incidences, fill = sex))+
  geom_col(fill = "darkgreen")+
  guides(fill = guide_legend("none"))+
  coord_flip()+
  labs(
    x = "Type of Cancer",
    y = "Incidences",
    title = "Male Cancer Incidences in the Borders"
  )+
  theme_classic()

healthboards_data %>% 
  filter(cancer_site != "All cancer types",
         hb == "NHS Borders",
         sex == "Female") %>% 
  group_by(cancer_site) %>%
  mutate(total_incidences = sum(incidences_all_ages)) %>% 
  slice_max(n = 1, order_by = total_incidences, with_ties = FALSE) %>% 
  arrange(desc(total_incidences)) %>% 
  head(10) %>% 
  ggplot(aes(x = cancer_site, y = total_incidences, fill = sex))+
  geom_col(fill = "darkorchid")+
  coord_flip()+
  guides(fill = guide_legend("none"))+
  labs(
    x = "Type of Cancer",
    y = "Incidences",
    title = "Female Cancer Incidences in the Borders"
  )+
  theme_classic()
```
From the findings of most common types of cancer per gender in the borders, the 
most common overall for both being skin cancer is clear. Unique cancers to each
gender, such as prostate and cervix are clearly shown to be large contributors
as well. 

</details>


<details>
<summary>  - See how cancer incidences have changed over the years </summary>


```{r, echo = FALSE, warning=FALSE}

healthboards_data %>% 
  filter(hb == "NHS Borders",
         cancer_site == "All cancer types",
         sex != "All") %>%
  ggplot(aes(x = year, colour = sex, y = incidences_all_ages))+
  geom_line()+
  labs(x = "Year",
       y = "Incidences",
       title = "Cancer Incidences in the Borders over the years")+
  theme_classic()

```

Unfortunately, consistent increases over the years, spikes for females could be 
related to regular checkups for cervical/breast cancer since the records began, 
approx every 3 years. 

Increase spikes for males could be related to marketing campaigns for getting
checked occurring and encouraging men to actually get checked for cancer. 

Consistent increase could be more to do with different kinds of cancer being 
discovered as well as better technology discovering it. 



```{r, echo = FALSE, warning=FALSE}

cancer_age_data %>% 
  group_by(incidence_age_range) %>%
  filter(sex != "All",
         incidence_age_range != "incidences_all_ages") %>% 
  mutate(incidence_age_range = recode(incidence_age_range,
                                      "5to9" = "05 to 09",
                                      "90and_over" = "90 and over",
                                      "85to89" = "85 to 89",
                                      "80to84" = "80 to 84",
                                      "75to79" = "70 to 79",
                                      "70to74" = "70 to 74",
                                      "65to69" = "65 to 69",
                                      "60to64" = "60 to 64",
                                      "55to59" = "55 to 59",
                                      "50to54" = "50 to 54",
                                      "45to49" = "45 to 49",
                                      "40to44" = "40 to 44",
                                      "35to39" = "35 to 39",
                                      "30to34" = "30 to 34",
                                      "25to29" = "25 to 29",
                                      "20to24" = "20 to 24",
                                      "15to19" = "15 to 19",
                                      "10to14" = "10 to 14",
                                      "_under5" = "00 to 04")) %>% 
  ggplot(aes(x = incidence_age_range, y = incidences_per_age_range))+
  geom_col()+
  coord_flip()+
  facet_wrap(~sex)+
  theme_classic()+
  labs(x = "Age Range",
       y = "Incidences",
       title = "Cancer Incidences by Age")
```


As for ages, it is clear that there is a significant increase of incidences 
when reaching a certain age, with the spike for both genders coming between 70 
and 79. 


</details>

